% Example on grouping the sensors in R
% Andrey Ziyatdinov
% 25/09/2014

```{r setup, include = FALSE}
opts_chunk$set(fig.path = 'figure/', cache.path = 'cache/', echo = TRUE, 
  cache = FALSE, tidy = FALSE,
  fig.width = 9, fig.height = 9, dev = 'png', fig.cap = "",
  warning = FALSE, message = FALSE)
opts_knit$set(upload.fun = identity)
```

## About

This document shows an example of code in R,
in order to read the `features.csv` of the `pulmon` data set published on 
[The UC Irvine Machine Learning Repository](http://archive.ics.uci.edu/ml/).

## How to reproduce this report

The working directory:
```{r}
getwd()
```

Run the following commands in R:

```
library(knitr)
knit2html("03-group-sensors.Rmd")
```

That results in two output files: `*.md` (for github) and `*.html` (for browsing locally on your computer).

## Data files

For this report the data files are stored in:

```{r}
dat.dir <- "../../../dat"

list.files(dat.dir)
```

One can change the path stored in `dat.dir` variable, if needed.

## Demo

```{r}
### inc
library(plyr)
library(ggplot2)

### options
options(stringsAsFactors = FALSE)
```

```{r, cache = TRUE}
### sensors' info
load(file.path(dat.dir, "pulmon.sensors.RData"))
```

```{r, cache = TRUE}
### data
dat <- read.table(file.path(dat.dir, "features.csv"), header = TRUE, sep = ",")
```

We are interested in `max` features.

```{r max}
ind <- grep("_max", colnames(dat))
X <- dat[, ind]

Y <- dat$lab
```

Filter out two labels: `ace-0.3 and `eth-0.3`.

```{r filter}
Xace <- X[Y == "ace-0.3", ]
Xeth <- X[Y == "eth-0.3", ]
```

```{r df}
df <- data.frame(sensor = 1:16,
  ace = apply(Xace, 2, mean),
  eth = apply(Xeth, 2, mean))
```

Plot affinity map.

```{r affinity_map}
p1 <- ggplot(df, aes(ace, eth)) + geom_text(aes(label = sensor)) +
  geom_abline(a = 0, b = 1)
p1
```

## Compare with sensors' info

```{r}
pulmon.sensors
```

One group of 4 sensors of type `10_5` (bottom-left corner on the figure):

```{r}
with(pulmon.sensors, R[class == "10_5"])
```

Another group of 4 sensors of type `10_3.3` (center-left part of the figure):

```{r}
with(pulmon.sensors, R[class == "10_3.3"])
```

